\textbf{Note:} The Zoom Transparency Tree is not currently available. We plan to release it in a
future update.

In this section, we describe a mechanism that expands the authentication guarantees from
Sections~\ref{sec:identitykeymanagement} and \ref{sec:idpattestations} to ensure that all Zoom users
have a consistent view of each others' devices and keys.

Imagine an insider, Mallory, who wants to eavesdrop on a meeting between honest users Alice and Bob,
who have never interacted on Zoom before and haven't checked the meeting leader security code. To
succeed in this attack, Mallory could instruct the Zoom server to lie to Alice about Bob's keys and
to Bob about Alice's keys, replacing them with keys she controls. If Bob's client is the only one to
see the fake key for Alice, and similarly Alice's is the only client who gets the fake key for Bob,
then such an attack would be hard to detect after the fact.

Some possible countermeasures for such attacks require trusted external entities or manual
validation steps (such as checking the security codes described in
Section~\ref{subsec:securitycode}) that potentially have to be performed out-of-band. Instead, we
will be able to detect equivocation by Zoom servers and identity providers while minimizing active
checking by the user.

To do so, we will ensure that Zoom servers provide the same mapping between user accounts and public
keys to all clients, sign such a mapping, and are held accountable for these signed statements. This
way, in order to compromise a single meeting, Zoom would have to lie not only to Alice about Bob's
keys (and vice versa), but also to every other Zoom user about those keys, including lying to Bob
about his own keys. Bob's client can thus easily review the list of his devices and discover any
suspicious activity. External auditors will routinely verify that the server's mapping is consistent
over time.

Thus, key fingerprint comparisons and other related warnings can be demoted in the user experience,
to be replaced with targeted security alerts (which we expect never to be triggered). Key security
becomes virtually invisible to the user.

\subsection{Zoom Transparency Tree}

The idea that there should be a single and consistent mapping between an identity and its public
keys has already been explored successfully to solve similar issues. Most notably, Certificate
Transparency~\cite{langley2013certificate} limits the damage that a compromised certificate
authority can do by signing fake TLS certificates. It does so by requiring that all signed X.509
certificates must be submitted to a publicly auditable log before being accepted by browsers.
Industry projects such as Key Transparency~\cite{keytransparency} and Keybase~\cite{keybase} (which
is now part of Zoom) and academic works such as SEEMless~\cite{chase2019seemless} and
CONIKS~\cite{melara2015coniks} have explored applying a similar approach to individual users'
identities for messaging applications, with Keybase being the only instance in production use today,
as far as we know. However, all the existing solutions in this space that we are aware of do not
currently match Zoom's security and privacy requirements while offering usability features like
multi-device support.

We build on prior work to design a new mechanism tailored to Zoom's use cases: the Zoom Transparency
Tree (ZTT). The ZTT is backed by a Merkle tree as used by Keybase, but with privacy-preserving
path-lookup features as in CONIKS. This data structure offers a key-value store interface where
key-value pairs, once inserted, cannot be removed or altered. The state of the structure can be
summarized by a small commitment, and lookup queries can be accompanied by a short proof that they
are consistent with the commitment. Whenever a client is given a signed sigchain statement (as
introduced in Section~\ref{subsec:sigchains}) about another user's identity or their keys, this
statement is accompanied by an inclusion proof in the ZTT.

\subsection{Integration Details}

\subsubsection{ZTT Auditing}\label{subsec:zttaudit}

The design of the ZTT requires auditing to verify the structure of the tree. Zoom will partner with
independent external auditors which (in a privacy-preserving way) ensure that the append-only
property of the ZTT is respected.

Clients query the auditors to ensure that their view of the ZTT's commitment has been audited and is
consistent with everyone else's. If the client can reach the auditor and detects a fork in the ZTT,
they can send the auditor the forked and signed commitments in addition to the warning, so that the
auditor can disclose the inconsistency. If Zoom clients cannot reach any of the auditor servers,
they will signal a degraded encryption level.

We will publish code so that interested parties can also audit the ZTT.

Additionally, organizations using Zoom will be able to review updates to the ZTT and track their
employees' device changes.

\subsubsection{Provisioning}

When provisioning a new device, the client ensures that the sigchain statement is included in the
ZTT by first sending it to the Zoom servers and then querying the ZTT to check that the sigchain
update has been included.

\subsubsection{Self-Audit and Refresh}

Periodically, the user's client should ask the server for an updated ZTT commitment, ensure that
this commitment is consistent with past data, possibly verify it with external auditors, and review
the user's sigchain for any new statements. If new keys are added to the sigchain, the client should
ask the user to review the changes. If the user notices an unexpected change, they may be prompted
to change their password or talk to their IT department.

\subsubsection{Validating User Identity}

Because we only trust keys stored within the ZTT, users can verify that each others' public keys are
included in the ZTT, before proceeding with using the keys.

\subsubsection{Contact List Updates}

The contact lists that users accumulate, described in Section~\ref{subsec:contactsync}, can also be
stored in the ZTT. The immutability guarantees that the ZTT provides means that Alice can note an
update to Bob's identity in the client installed on her phone, and Zoom is obliged to relay that
update to her desktop client.

\subsection{Security Properties}

Though the ZTT allows an equivocating server to be detected, we rely on the user to validate device
additions. Users might be offline or might be ignoring notifications and therefore compromises might
not be detected, or only detected after an attack.

The ZTT requires external auditors to provide security guarantees. If the auditors are not honest,
or have poor uptime, this can limit the ability to detect server misconduct. We can mitigate this
risk by relying on multiple auditors or implement partial auditing by clients.
